\documentclass[11pt]{article}
%\documentclass[11pt]{amsart}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{amsmath,amssymb,latexsym}
\usepackage{epstopdf}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\title{Rifidi Auto-Builder}
\author{James Percent \\ james@pramari.com}
\date{\today}                                          % Activate to display a given date or no date

\begin{document}
\maketitle

\tableofcontents
\listoffigures

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}

We like working in PDE, but we need automated builds for our enviornment.   PDE builder sucks, and we like to program, so we wrote a quick script to generate Ant-based build files for our project.

Why.



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Python}\label{os}

We implemented the script in python.  We like Python because...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Usage}

Talk about how to use the script and what it does.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Design}

Talk about how the script works.  The design concepts.

\section{Code}

\section{Bugs and Odities}
The code currently has a few quarks.  Does not handle gnu-io as PDE does.  I made a dumby jar for building Gnu\_io

\begin{itemize}

\item Jars added to the project as libs.  These Jars must be in the lib directory, at the same level as the META-INF folder 
or they will not be found and used
\item Doesn't handle parsing regular Jar files.
\item Doesn't handle parsing bundles of Jars.  For example, the GNU IO package is not handle properly by default.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage

\begin{thebibliography}{99}
\bibitem{ubuntu} Ubuntu Releases.  \url{http://releases.ubuntu.com}.
\bibitem{lucid} Ubuntu 10.04.1.  \url{http://releases.ubuntu.com/lucid}.
\bibitem{lucid-doc} Ubuntu 10.04.1 Documentation. \url{https://help.ubuntu.com/10.04/index.html}.
\bibitem{apt-get-tut} Apt.  \url{http://www.debian.org/doc/manuals/apt-howto/ch-apt-get.en.html}.
\bibitem{webmail}  Webmail.  \url{http://webmail.textdrivehosting.com/index.php}.
\bibitem{thunderbird} Thunderbird. \url{http://www.mozilla.org/projects/thunderbird}.
\bibitem{harwood} Mail server \url{harwood.textdrive.com}.
\bibitem{basecamp} Pramari Basecamp.  \url{https://pramari.basecamphq.com}.
\bibitem{rallydev}  Rally.  \url{https://community.rallydev.com}.
\bibitem{scrum-book}  Schwaber, Ken. Agile Project Management with Scrum.
\bibitem{scrum-guide} Scrum Guide.  \url{http://www.scrum.org/scrumguideenglish}. 
\bibitem{rep-edge} RIFIDI Edge Server. \url{https://svn.rifidi.org/svn/rep-edge}.
\bibitem{rep-external} RIFIDI Toolkit. \url{https://svn.rifidi.org/svn/rep-external}.
%\bibitem{rep-internal} RIFIDI ?? . \url{https://svn.rifidi.org/svn/rep-internal}.
\bibitem{rep-ambient} Ambient Project. \url{https://svn.rifidi.org/svn/rep-ambient}.
\bibitem{eclipse} Eclipse.  \url{http://www.eclipse.org.}.
\bibitem{pde} Plug-in Development Environment.  \url{http://www.eclipse.org/pde/}.
\bibitem{osgi-book} OSGI and Equinox: Creating Highly Modular Javaª Systems.  \url{http://equinoxosgi.org}.
\bibitem{equinox} Equinox.  \url{http://www.eclipse.org/equinox}.
\bibitem{osgi} OSGi Alliance. \url{http://www.osgi.org/Main/HomePage}.	
\bibitem{spring-dm} Spring Dynamic Modules for OSGi Service Platforms.  \url{http://www.springsource.org/osgi}.
\bibitem{galileo} Eclipse Galileo.  \url{http://download.eclipse.org/releases/galileo}
\bibitem{subclipse} Subclipse.  \url{http://subclipse.tigris.org/}.
\bibitem{di} Fowler, M.  Dependency Injection.  \url{http://martinfowler.com/articles/injection.html}.
\bibitem{subclipse-doc} Subclipse online documentation.  \url{http://svn.collab.net/subclipse/help/index.jsp}.
\bibitem{subclipse-update} Subclipse.  \url{http://subclipse.tigris.org/update_1.6.x}.
\end{thebibliography}
\end{document}  


